---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# velo_apps
`velo_apps` provides functions of the [velo](https://github.com/jannes-m/velo)-package as RShiny Apps. This way people unfamiliar with R can now easily use `velo`-functions.

* `spoke_app` calculates spoke lengths.
* `fixie_teeth` calculates for a given gear ratio the optimal combination of cog ring teeth and chainring teeth in terms of skid patches.


To run `velo`-apps locally, use function `runGithub`. Taking spoke_app as an example, you can run:
```{r, eval = FALSE}
shiny::runGitHub("velo_apps", "jannes-m", subdir = "spoke_length")
```

Another possibility is to clone the velo_apps-repository to your local computer. Use `shiny::runApp("spoke_app")` to run the app.

# Still to do

1. `spoke_length`: (visual) description of the measures to take (e.g., ERD, hub to left flange, etc.)
2. write `fixie_app` for Olli
3. write `trail_app` together with Dirk

